Approximation as Differentiation notes

### 2025-02-09 notes.tex
Define Fam.

@@

@@

This is the Grothendieck construction for a functor $F: C \to \Cat$, in the special case where $F: C \to
\Set$. (Where we read a $\Set$-valued functor as a $\Cat$-valued functor restricted to discrete categories.)

>>>>

$\Set$ will often be $\Setoid$ in the Agda code but we'll ignore that here for now.

@@

\subsection{Indexed families of objects}

For $I$ a set and $C$ a category, write $\Fam(I,C)$ for the set of $I$-indexed families of objects of $C$.

Suppose $C$ a category and $I, J$ sets and $x$ an $I$-indexed family of objects of $C$ and $y$ a $J$-indexed
family of objects of $C$. Define $y_f$ for any $f: I \to J$ to be the $I$-indexed family of objects of $C$.

@@

For a functor $F: C \to Set$, we have the category where:
\begin{itemize}
\item objects are pairs $(I, x)$ with $I$ an object of $C$ and $x \in FI$
\item morphisms from $(I, x)$ to $(J, y)$ are morphisms $f: I \to J$ in $C$ where $(Ff)(x) = y$
\end{itemize}

\noindent This is the Grothendieck construction for a functor $F: C \to \Cat$, in the special case where $F: C
\to \Set$. (Where we read a $\Set$-valued functor as a $\Cat$-valued functor restricted to discrete
categories.)

In our code we give a slightly different construction. For a category $C$, define the category where:
\begin{itemize}
\item objects are pairs $(I, x)$ with $I$ a set and $x$ an $I$-indexed family of objects of $C$
\item morphisms from $(I, x)$ to $(J, y)$ are functions $f: I \to J$ paired with morphisms
\end{itemize}
